The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-18 paper.tex
Added a comment of the figure 'qualitative score vs interactions'

\title[Dynamics of Anthropomorphism]{Dynamics of Anthropomorphic Effects in Human-Robot Interaction}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}
\topic{The Uncanny Valley Hypothesis and Beyond}% If your article is part of a Research Topic, please indicate here which.

@@

\section{Anthropomorphism as a multi-factor phenomenon ...}
\label{sec:multi-factors}

@@

\section{... that evolves over time}
\label{sec:dynamics-model}

@@

Measuring anthropomorphism is challenging because the phenomenon is partialy
unconscious, its mediation is largely subject-dependent, and we found the
phenomenon generally difficult to verbalize for users.

@@

\begin{itemize}
    \item Spontaneously ascribe feelings or states (2 points) {\it Robot is
        hungry, tired}
    \item Ascribe ``own will'' (1--3 points) {\it Robot could leave room, does not
        always obey, could do a b\^{e}tise...}
    \item View robot as friend (1 point)
    \item Ascribe cognitive abilities (0.5--1 point) {\it Robot is able to see,
        able to hear}
    \item Belief robot has feelings (2 points)
    \item Give anthropomorphic reasons for
        \begin{itemize}
            \item not leaving robot alone (1--3 points) {\it Would be sad when
                left alone}
            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn’t
                like to play any longer}
        \end{itemize}
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{ranger-interactions-per-runs}
    \caption{Quantitative assessment: here, six interactions modalities have
        been selected: showing something to the robot ({\tt show}), talking to
        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
        shaking it, {\tt mis}), deictic interactions ({\tt ges}), and looking
        for exterior help by looking at the experimenter ({\tt look}). In each
        of the 14 experimental runs, we annotate and count the number of
        occurences of each of these interactions.  Highlighted runs 2.3, 2.4,
        2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
        of interactions everytime the robot's behaviour changes from expected to
        unexpected or from unexpected to expected.}

@@

@@

\subsection{Initialization Phase}
\label{sec:initialization}

@@

\subsection{Familiarization Phase}
\label{sec:familiarization}

@@

\subsection{Stabilization Phase}
\label{sec:stabilization}

>>>>

\title[The Dynamics of Anthropomorphism]{The Dynamics of Anthropomorphic Effects in Human-Robot Interaction}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}
\topic{The Uncanny Valley Hypothesis and Beyond}% If your article is part of a Research Topic, please indicate here which.

@@

\subsection{Summary: Anthropomorphism as a multi-factor phenomenon}
\label{sec:multi-factors}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{factors}
    \caption{}
    \label{factors}
\end{figure}

\section{Anthropomorphism: a dynamic phenomenon}
\label{sec:our-ideas}

@@

Measuring anthropomorphism is challenging because the phenomenon is partially
unconscious, its mediation is largely subject-dependent\fxnote{Should we put
here different interaction profiles from the Ranger study?}, and we found the
phenomenon generally difficult to verbalize for users.

@@

\begin{itemize}
    \item Spontaneously ascribe feelings or states (2 points) {\it Robot is
        hungry, tired}
    \item Ascribe ``own will'' (1--3 points) {\it Robot could leave room, does not
        always obey, could do a b\^{e}tise...}
    \item View robot as friend (1 point)
    \item Ascribe cognitive abilities (0.5--1 point) {\it Robot is able to see,
        able to hear}
    \item Belief robot has feelings (2 points)
    \item Give anthropomorphic reasons for
        \begin{itemize}
            \item not leaving robot alone (1--3 points) {\it Would be sad when
                left alone}
            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn't
                like to play any longer}
        \end{itemize}
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{ranger-interactions-per-runs}
    \caption{Quantitative assessment: here, six interactions modalities have
        been selected: showing something to the robot ({\tt show}), talking to
        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
        shaking it, {\tt mis}), deictic interactions ({\tt ges}), and looking
        for exterior help by looking at the experimenter ({\tt look}). In each
        of the 14 experimental runs, we annotate and count the number of
        occurrences of each of these interactions.  Highlighted runs 2.3, 2.4,
        2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
        of interactions every time the robot's behaviour changes from expected to
        unexpected or from unexpected to expected.}

@@

Fig.~\ref{qualitative-score} plots the qualitative vs quantitative assessment of
anthropomorphic effects during the \emph{Dominos} experiment: the correlation is
negative. The more the children interacted with the robot, the less they
projected anthropomorphic traits on the robot. We also note a remarkable cluster
of seven groups of children who did not interact much with the robot, but had a
strongly anthropomorphic perception of the robot. This may initially look
counter-intuitive (one could hypothesize that the more playful the children are
with the robot, the more likely they are to consider it as a friend/pet/lively
being) and we discuss at section~\ref{sec:cognition-neuroscience} possible
cognitive explanations.

@@

\subsubsection{Initialization Phase}
\label{sec:initialization}

@@

\subsubsection{Familiarization Phase}
\label{sec:familiarization}

@@

\subsubsection{Stabilization Phase}
\label{sec:stabilization}
